The imprint of global magma oceans on exoplanet demographics

### 2023-02-15 src/tex/ms.tex
uniform prior for S_thresh

A sensible choice of priors is central for evidence estimation via nested sampling.
As the parameters we are interested in recovering, $S_\mathrm{thresh}$ and $x_{H_2O}$, are poorly constrained by previous data, we used relatively uninformative priors to sample the entire physically plausible parameter space.
For $S_\mathrm{thresh}$, we chose a log-uniform prior in $[\prSmin,\prSmax]\, \SI{}{\watt\per\meter\squared}$.
Similarly, we sample $x_{H_2O}$ from a log-uniform distribution to imply scale-invariant ignorance.
Its boundaries $[\prWRRmin, \prWRRmax]$ are motivated by the water mass fractions covered by the geophysical models~(Sect.~\ref{sec:mo_model}).
Finally, we adopt a broad, uniform prior for $\langle R_\mathrm{P}\rangle_\mathrm{out}$ bound by $[\prRmin, \prRmax] \, \mathrm{R_\oplus}$.
We then ran the nested sampler to compute the evidence and sample the posterior distributions.

>>>>

A sensible choice of priors is central for evidence estimation via nested sampling.
As the parameters we are interested in recovering, $S_\mathrm{thresh}$ and $x_{H_2O}$, are poorly constrained by previous data, we used relatively uninformative priors to sample the entire physically plausible parameter space.
For $S_\mathrm{thresh}$, we chose a uniform prior in $[\prSmin,\prSmax]\, \SI{}{\watt\per\meter\squared}$.
We sample $x_{H_2O}$ from a log-uniform distribution to imply scale-invariant ignorance.
Its boundaries $[\prWRRmin, \prWRRmax]$ are motivated by the water mass fractions covered by the geophysical models~(Sect.~\ref{sec:mo_model}).
Finally, we adopt a broad, uniform prior for $\langle R_\mathrm{P}\rangle_\mathrm{out}$ bound by $[\prRmin, \prRmax] \, \mathrm{R_\oplus}$.
We then ran the nested sampler to compute the evidence and sample the posterior distributions.
